The Evolution of Phenotypically Invariant Genetic Networks

### 2017-03-29 kalman_walk.tex
added questions about rube goldgergness and network ratchets

>>>>

\section{Network Ratchet}

If a network evolves to include more molecules (such as transcription factors) and thus becomes higher dimensional, can the network also remove these originally superfluous interactions or will removing these typically lead to catastrophic network dysfunction after some amount of evolutionary time and system drift has occured?

\section{Network Minimality versus Rube Goldbergness}

Are there evolutionary differences between realizing a transfer function minimally (with a reachable and observable system) or non-minimally (a system with unreachable and/or unobservable subspaces)? Can reducible systems be more or less mutationally robust? Are minimal systems energetically more efficient? Are reducible systems more or less evolvable?
